Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-03 xrb/paper.tex
add Simons affiliation

\author[0000-0001-8401-030X]{Michael Zingale}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
             Stony Brook, NY 11794-3800}

@@

\acknowledgements \castro\ is open-source and freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The problem setups used
here are available in the git repo as {\tt flame} and {\tt
  flame\_wave}.  The work at Stony Brook was supported by DOE/Office
of Nuclear Physics grant DE-FG02-87ER40317.  YC was supported by the
European Union Horizon 2020 research and innovation program under
the Marie Sklodowska-Curie Global Fellowship grant agreement No.\
703916.  This research used resources of the National Energy Research
Scientific Computing Center, a DOE Office of Science User Facility
supported by the Office of Science of the U.~S.\ Department of Energy
under Contract No.\ DE-AC02-05CH11231.  This research used resources
of the Oak Ridge Leadership Computing Facility at the Oak Ridge
National Laboratory, which is supported by the Office of Science of
the U.S. Department of Energy under Contract No. DE-AC05-00OR22725,
awarded through the DOE INCITE program.  This research has made use of
NASA's Astrophysics Data System Bibliographic Services.

>>>>

\author[0000-0001-8401-030X]{Michael Zingale}
\affiliation{Dept.\ of Physics and Astronomy, Stony Brook University,
             Stony Brook, NY 11794-3800}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, New York, NY 10010}

@@

\acknowledgements \castro\ is open-source and freely available at
\url{http://github.com/AMReX-Astro/Castro}.  The problem setups used
here are available in the git repo as {\tt flame} and {\tt
  flame\_wave}.  The work at Stony Brook was supported by DOE/Office
of Nuclear Physics grant DE-FG02-87ER40317 and the SciDAC program DOE grant DE-SC0017955.  MZ acknowledges support
from the Simons Foundation.  YC was supported by the
European Union Horizon 2020 research and innovation program under
the Marie Sklodowska-Curie Global Fellowship grant agreement No.\
703916.  This research used resources of the National Energy Research
Scientific Computing Center, a DOE Office of Science User Facility
supported by the Office of Science of the U.~S.\ Department of Energy
under Contract No.\ DE-AC02-05CH11231.  This research used resources
of the Oak Ridge Leadership Computing Facility at the Oak Ridge
National Laboratory, which is supported by the Office of Science of
the U.S. Department of Energy under Contract No. DE-AC05-00OR22725,
awarded through the DOE INCITE program.  This research has made use of
NASA's Astrophysics Data System Bibliographic Services.
